Blowship - Anonymous Communication via a Central Server

### 2014-03-10 paper.tex
Im sure there are some changes

\section*{Abstract} 
  Many systems have been developed that preserve the anonymity of the sender and receiver of data. These systems are typically decentralized, routing messages through some series of trusted or untrusted peers and servers.

@@

 In p2p protocols, delivering a message via a chain of peers or servers is common: Mix-based systems use cascades and mix networks, onion-based systems create circuits, etc. In this system we'll use the onion routing terminology and call the chain of peers a message passes through a $circuit$.

@@

Fortunately, due to the nature of this system we can provide almost complete protection with \textbf{cover traffic} \cite{trickle02}, or having each peer send dummy messages along with the messages it's forwarding. If done correctly in this model, a peer should at minimum send one dummy message along with every real message, maintaining a branching factor of two at every hop. Typically providing complete protection with cover traffic is difficult - it requires the mix to choose dummy message recipients uniformally from all users. In our system, however, randomly and anonymously choosing other online peers is designed to be efficient.

It would also be possible to use inter-mix detours\cite{TODO}, or having peers randomly decide to introduce new hops to prevent Surge from recognizing his own messages sent during an $n - 1$ attack. However, this reduces reliability, increases latency, and given the protection that cover traffic provides seems unnecessary in this system.

@@

\section{Future Work}
\begin{enumerate}
  \item \textbf{Pseudonymity.} Allow for parties to communicate securely without knowing eachother's identities.
  \item \textbf{Faster circuits.} Like Tor, we could use layers of symmetric encryption between successive pairs of peers in a circuit. Using a public/symmetric system like Tor could help with pseudonymity as well.
  \item \textbf{DoS.} We'd like to prevent DoS attacks by requiring some proof of work etc for messages being sent. 
\end{enumerate}

>>>>

\section*{Abstract} 
  Mzany systems have been developed that preserve the anonymity of the sender and receiver of data. These systems are typically decentralized, routing messages through some series of trusted or untrusted peers and servers.

@@

 In p2p protocols, delivering a message via a chain of peers or servers is a standard method to achieve anonymity. In this system we'll use terminology from Tor and call the chain of peers a message passes through a $circuit$. A pseudo-p2p circuit then consists of an alternating chain of peer-server and server-peer communications.

@@

Fortunately, due to the nature of this system we can provide almost complete protection with \textbf{cover traffic} \cite{trickle02}, or having each peer send dummy messages along with the messages it's forwarding. A peer will at minimum send one dummy message along with every real message, maintaining a branching factor greater than two at every hop. Typically providing complete protection with cover traffic is difficult - it requires the mix to choose dummy message recipients uniformally from all users. In our system, however, randomly and anonymously choosing other online peers is designed to be efficient.

It would also be possible to use inter-mix detours\cite{TODO}, having peers randomly decide to introduce new hops to prevent Surge from recognizing his own messages sent during an $n - 1$ attack. However, this reduces reliability, increases latency, and given the protection that cover traffic provides seems unnecessary in this system.

@@

\section{Future Work}
\begin{description}
  \item[Pseudonymity.] Allow for parties to communicate securely without knowing eachother's identities.
  \item[Faster circuits.] Like Tor, we could use layers of symmetric encryption between successive pairs of peers in a circuit. Using a public/symmetric system like Tor could help with pseudonymity as well.
  \item[DoS.] We'd like to prevent DoS attacks by requiring some proof of work etc for messages being sent.
\end{description}
